\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{booktabs}

\title{Analysis of Consumer Financial Fraud and Prevention Strategies \\
\large CIS 3319: Wireless Networks and Security / CIS 4378: Computer and Network Security \\
\large Lab 1: Consumer Financial Fraud Investigation}
\author{Group Members: \\ Aaron Jefferson \\ }
\date{01-Feb-2024}

\begin{document}

\maketitle

\begin{abstract}
\noindent Provide a brief summary of the report, including key findings and conclusions.
\end{abstract}

\tableofcontents

\section{Introduction}
Provide an overview of the report's purpose, the importance of understanding consumer financial fraud, and an overview of your methodology.

\section{Exploration of Consumer Financial Fraud}
\subsection{Examples and Analysis}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Source} & \textbf{Brief Description} & \textbf{Vulnerabilities} & \textbf{Attack Vectors} \\ \midrule
www.example.com & Description & Vulnerability & Attack Vector \\
% Add more rows as needed
\bottomrule
\end{tabular}

Discuss each example in detail, focusing on how the fraud was perpetrated.

\subsection{Common Vulnerabilities and Attack Vectors}
Summarize the common vulnerabilities and attack vectors identified in the examples.

\section{Prevention Advice Analysis}
\subsection{Examples of Advice}
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Source} & \textbf{Advice} \\ \midrule
www.example.com & 1. Advice 1 \\ 
                & 2. Advice 2 \\
% Add more rows as needed
\bottomrule
\end{tabular}

Discuss each piece of advice, ensuring clarity for a general audience.

\subsection{Summary of Common Advice}
Summarize the common pieces of advice identified.

\section{Effectiveness of Prevention Strategies}
\subsection{Analysis of Advice Against Vulnerabilities}
Assess how each piece of advice addresses the vulnerabilities and attack vectors.

\subsection{Limitations and Unaddressed Threats}
Identify any advice that does not target vulnerabilities or attack vectors, and highlight any attacks not defended by the advice.

\subsection{Tailoring Advice for Specific Populations}
Discuss how advice might need modification for older adults, non-native English speakers, visually impaired users, etc.

\section{Conclusion}
Summarize the key findings, the effectiveness of current advice, and any recommendations for improvement.

\section{References}
List all sources used in your report.

\end{document}
